---
title: "CLT"
author: "Cadence Gorden"
date: "2022-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000<- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex))+
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
                color="blue", linetype="dashed", size=1)
print(paste('mean= ', mean(my1000$kkardashtemp),' sd= ',sd(my1000$kkardastemp)))
```

This graph shows us that there is not a normal solution but a bimodal solution. We know this because there is two normal solutions which mean bimodal. 

```{r}
numb=2
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T), "kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol = numb)
x.avg<- apply(mdata,1,mean)
my1000$k2 =x.avg

p<- ggplot(my1000, aes(x=k2)) +
  geom_density()
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
             color="blue", linetype="dashed", size=1)
print(paste('mean= ', mean(my1000$k20),' sd = ',sd(my1000$k2)))
```

```{r}
numb= 4
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T), "kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol = numb)
x.avg<- apply(mdata,1,mean)
my1000$k4 =x.avg


p <- ggplot(my1000, aes(x=k4), col=sex) +
  geom_density()+
  
  #Add mean line
  geom_vline(aes(xintercept=mean(k4)),
             color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k4), ' sd = ',sd(my1000$k4)))
```

```{r}
numb= 9
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T), "kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol = numb)
x.avg<- apply(mdata,1,mean)
my1000$k9 =x.avg


p <- ggplot(my1000, aes(x=k9), col=sex) +
  geom_density()+
  
  #Add mean line
  geom_vline(aes(xintercept=mean(k9)),
             color="blue", linetype="dashed", size=1)
p + ggtitle("n = 9") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k9), ' sd = ',sd(my1000$k9)))
```

```{r}
options(digits = 2)
```
In this graph theres one peak. The mean is 'r mean(my1000$k9)' and the sd is 'r sd(my1000$k9)'

```{r}
numb= 16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T), "kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol = numb)
x.avg<- apply(mdata,1,mean)
my1000$k16 =x.avg


p <- ggplot(my1000, aes(x=k16), col=sex) +
  geom_density()+
  
  #Add mean line
  geom_vline(aes(xintercept=mean(k16)),
             color="blue", linetype="dashed", size=1)
p + ggtitle("n = 16") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k9), ' sd = ',sd(my1000$k9)))
```
This graph also only has one peak, so that means the mean is 'r mean(my1000$k16)' and the sd is 'r sd(my1000$k16)'. 

```{r}
numb= 25
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T), "kkardashtemp"]
mdata <-matrix(Hdata,nrow=1000,ncol = numb)
x.avg<- apply(mdata,1,mean)
my1000$k25 =x.avg


p <- ggplot(my1000, aes(x=k25), col=sex) +
  geom_density()+
  
  #Add mean line
  geom_vline(aes(xintercept=mean(k25)),
             color="blue", linetype="dashed", size=1)
p + ggtitle("n = 2") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k9), ' sd = ',sd(my1000$k9)))
```

By looking at the pattern of results, all the graph are only going to have one peak. This means the mean is going to be 'r mean(my1000$k25)' and the sd is going to be 'r sd(my1000$k25)'. 