---
title: "CLT"
author: "Cadence Gorden"
date: "2022-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")
ggplot(Homers_data, aes(x=kkardashtemp, fill=sex)) + geom_density()
```

This graph shows us that there is not a normal solution but a bimodal solution. We know this because there is two normal solutions which mean bimodal. 

```{r}
guys<-filter(Homers_data, sex=="male") 

```


```{r}
Homers_data <- read.csv(file="Homers_data.csv")
guys1000 <- sample(guys$kkardashtemp ,size = 1000, replace=T)
densityplot(guys1000,main="original data")

```


This graph shows us the guys are voting her in the 100's which means this is not a normal solution. It is a right skewed distribution. 

```{r}
girls<-filter(Homers_data, sex=="female") 

```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
girls1000 <- sample(girls$kkardashtemp ,size = 1000, replace=T)
densityplot(girls1000,main="original data")

```

This graph shows us the girls are voting her low which means it is still not a normal solution but a left skewed distribution. 


```{r}
basicCN <- ggplot(Homers_data,aes(x=kkardashtemp,col=sex))+geom_density()

```

